---
title: "DAII 3.5 AI Investment Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: flatly
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(DT)
library(ggplot2)
library(dplyr)
library(tidyr)
library(shiny)

# Set working directory to project root
setwd("C:/Users/sganesan/DAII-3.5-Framework")

# Auto-detect the latest run directory
run_dirs <- list.files("outputs", pattern = "run_", full.names = TRUE)

if(length(run_dirs) == 0) {
  stop("No run folders found in outputs directory. Please run the pipeline first.")
}

latest_run <- run_dirs[which.max(file.info(run_dirs)$mtime)]
run_timestamp <- gsub("run_", "", basename(latest_run))

cat("Loading data from:", basename(latest_run), "\n")

# Define file paths with error handling
load_data_file <- function(filename, required = TRUE) {
  file_path <- file.path(latest_run, paste0(run_timestamp, filename))
  if(file.exists(file_path)) {
    cat("  ✓ Loaded:", filename, "\n")
    return(read.csv(file_path))
  } else {
    if(required) {
      stop("Required file not found: ", filename)
    } else {
      cat("  ⚠️ File not found (skipping):", filename, "\n")
      return(NULL)
    }
  }
}

# Load data - mark optional files with required = FALSE
features <- load_data_file("_01_company_features_full.csv", required = TRUE)
unicorns <- load_data_file("_18_unicorn_watchlist.csv", required = FALSE)
benchmark_ai <- load_data_file("_23_benchmark_ai_exposure.csv", required = FALSE)
sector_ai <- load_data_file("_24_sp500_sector_ai_exposure.csv", required = FALSE)
portfolio_conc <- load_data_file("_20_portfolio_concentration.csv", required = FALSE)
discovery_full <- load_data_file("_10_discovery_full_universe.csv", required = FALSE)
anomaly_scores <- load_data_file("_11_anomaly_scores_full.csv", required = FALSE)

# Add company names from features
if(!is.null(unicorns) && !"company_name" %in% names(unicorns) && "company_name" %in% names(features)) {
  unicorns <- unicorns %>% left_join(features %>% select(ticker, company_name), by = "ticker")
}

# Top AI leaders
top_ai_leaders <- features %>% arrange(desc(ai_score)) %>% head(20)

# Calculate counts
total_companies <- nrow(features)
ai_leaders <- sum(features$ai_label == "AI Leader", na.rm = TRUE)
unicorn_count <- if(!is.null(unicorns)) nrow(unicorns) else 0
anomaly_count <- if(!is.null(anomaly_scores)) sum(anomaly_scores$is_anomaly, na.rm = TRUE) else sum(features$is_anomaly, na.rm = TRUE)
```r
# Recalculation function for custom weights
current_weights <- reactiveValues(
  rd = 0.30,
  patent = 0.30,
  growth = 0.20,
  stability = 0.20
)

recalculate_scores <- function(data, weights) {
  data %>%
    mutate(
      rd_quartile = ntile(rd_intensity, 4),
      patent_quartile = ntile(patent_activity, 4),
      growth_quartile = ntile(revenue_growth, 4),
      volatility_quartile = ntile(volatility, 4),
      rd_score_norm = rd_quartile * 25,
      patent_score_norm = patent_quartile * 25,
      growth_score_norm = growth_quartile * 25,
      stability_score_norm = (5 - volatility_quartile) * 25,
      innovation_score_custom = (rd_score_norm * weights$rd +
                                 patent_score_norm * weights$patent +
                                 growth_score_norm * weights$growth +
                                 stability_score_norm * weights$stability) / 100,
      ai_score_custom = innovation_score_custom * multiplier,
      ai_label_custom = case_when(
        ai_score_custom > 0.75 ~ "AI Leader",
        ai_score_custom > 0.5 ~ "AI Adopter",
        ai_score_custom > 0.25 ~ "AI Follower",
        TRUE ~ "AI Laggard"
      )
    )
}
```
Sidebar {.sidebar}
=======================================================================

### 🎯 AI Score Weighting Adjustments

Adjust the weights to see how AI scores change. Default weights are R&D=30%, Patents=30%, Growth=20%, Stability=20%.

```{r}
sliderInput("weight_rd", "R&D Intensity Weight:", 
            min = 0, max = 0.5, value = 0.30, step = 0.05)

sliderInput("weight_patent", "Patent Activity Weight:", 
            min = 0, max = 0.5, value = 0.30, step = 0.05)

sliderInput("weight_growth", "Revenue Growth Weight:", 
            min = 0, max = 0.5, value = 0.20, step = 0.05)

sliderInput("weight_stability", "Stability Weight:", 
            min = 0, max = 0.5, value = 0.20, step = 0.05)

actionButton("apply_weights", "Apply Custom Weights", class = "btn-primary")
actionButton("reset_weights", "Reset to Default", class = "btn-default")

hr()

h4("Current Weights in Use"),
verbatimTextOutput("weight_display")

hr()

h4("Patent Quality Flag"),
p("Companies with suspicious patent counts are flagged for manual review."),
p(strong("Highly Suspicious:"), " >100,000 patents (likely inflated)"),
p(strong("Suspicious:"), " 50,000-100,000 patents"),
p(strong("OK:"), " <50,000 patents")

KPI Row
=======================================================================

### Total Companies
```{r}
valueBox(total_companies, icon = "fa-building", color = "primary")
```

### AI Leaders
```{r}
valueBox(ai_leaders, icon = "fa-star", color = "success")
```

### Unicorn Candidates
```{r}
valueBox(unicorn_count, icon = "fa-unicorn", color = "warning")
```

### Anomalies Detected
```{r}
valueBox(anomaly_count, icon = "fa-exclamation-triangle", color = "danger")
```

AI Leaders Overview
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### Top AI Leaders Chart
```{r}
output$weight_display <- renderText({
  paste0("R&D: ", current_weights$rd * 100, "%\n",
         "Patent: ", current_weights$patent * 100, "%\n",
         "Growth: ", current_weights$growth * 100, "%\n",
         "Stability: ", current_weights$stability * 100, "%\n",
         "Total: ", (current_weights$rd + current_weights$patent + 
                     current_weights$growth + current_weights$stability) * 100, "%")
})

observeEvent(input$apply_weights, {
  current_weights$rd <- input$weight_rd
  current_weights$patent <- input$weight_patent
  current_weights$growth <- input$weight_growth
  current_weights$stability <- input$weight_stability
  
  if(!is.null(features) && "ai_score" %in% names(features) && nrow(top_ai_leaders) > 0) {
    features_custom <- recalculate_scores(features, current_weights)
    top_ai_leaders_custom <- features_custom %>% arrange(desc(ai_score_custom)) %>% head(20)
    
    output$ai_leaders_chart <- renderPlotly({
      plot_ly(data = top_ai_leaders_custom, x = ~reorder(company_name, ai_score_custom), y = ~ai_score_custom, type = "bar", marker = list(color = "#2c3e50"), text = ~paste("AI Score:", round(ai_score_custom, 3)), hoverinfo = "text") %>% layout(title = "Top 20 AI Leaders (Custom Weights)", xaxis = list(title = "", tickangle = -45), yaxis = list(title = "AI Score", range = c(0, 1.5)), margin = list(b = 100))
    })
    
    output$ai_leaders_table <- renderDT({
      top_ai_leaders_custom %>% select(ticker, company_name, ai_score_custom, innovation_score_custom, ai_label_custom) %>% mutate(ai_score_custom = round(ai_score_custom, 3), innovation_score_custom = round(innovation_score_custom, 3)) %>% datatable(colnames = c("Ticker", "Company", "AI Score", "Innovation", "Label"), options = list(pageLength = 10, dom = "Bfrtip", buttons = c("copy", "csv", "excel")), extensions = "Buttons", rownames = FALSE)
    })
  } else {
    cat("⚠️ AI leader data not available.\n")
  }
})

observeEvent(input$reset_weights, {
  updateSliderInput(session, "weight_rd", value = 0.30)
  updateSliderInput(session, "weight_patent", value = 0.30)
  updateSliderInput(session, "weight_growth", value = 0.20)
  updateSliderInput(session, "weight_stability", value = 0.20)
  
  current_weights$rd <- 0.30
  current_weights$patent <- 0.30
  current_weights$growth <- 0.20
  current_weights$stability <- 0.20
  
  if(!is.null(features) && "ai_score" %in% names(features) && nrow(top_ai_leaders) > 0) {
    features_custom <- recalculate_scores(features, current_weights)
    top_ai_leaders_custom <- features_custom %>% arrange(desc(ai_score_custom)) %>% head(20)
    
    output$ai_leaders_chart <- renderPlotly({
      plot_ly(data = top_ai_leaders_custom, x = ~reorder(company_name, ai_score_custom), y = ~ai_score_custom, type = "bar", marker = list(color = "#2c3e50"), text = ~paste("AI Score:", round(ai_score_custom, 3)), hoverinfo = "text") %>% layout(title = "Top 20 AI Leaders", xaxis = list(title = "", tickangle = -45), yaxis = list(title = "AI Score", range = c(0, 1.5)), margin = list(b = 100))
    })
    
    output$ai_leaders_table <- renderDT({
      top_ai_leaders_custom %>% select(ticker, company_name, ai_score_custom, innovation_score_custom, ai_label_custom) %>% mutate(ai_score_custom = round(ai_score_custom, 3), innovation_score_custom = round(innovation_score_custom, 3)) %>% datatable(colnames = c("Ticker", "Company", "AI Score", "Innovation", "Label"), options = list(pageLength = 10, dom = "Bfrtip", buttons = c("copy", "csv", "excel")), extensions = "Buttons", rownames = FALSE)
    })
  } else {
    cat("⚠️ AI leader data not available.\n")
  }
})

if(!is.null(features) && "ai_score" %in% names(features) && nrow(top_ai_leaders) > 0) {
  output$ai_leaders_chart <- renderPlotly({
    plot_ly(data = top_ai_leaders, x = ~reorder(company_name, ai_score), y = ~ai_score, type = "bar", marker = list(color = "#2c3e50"), text = ~paste("AI Score:", round(ai_score, 3)), hoverinfo = "text") %>% layout(title = "Top 20 AI Leaders", xaxis = list(title = "", tickangle = -45), yaxis = list(title = "AI Score", range = c(0, 1.5)), margin = list(b = 100))
  })
} else {
  cat("⚠️ AI leader data not available.\n")
}
```

### AI Score Distribution
```{r}
plot_ly(data = features, x = ~ai_score, type = "histogram", nbinsx = 30, marker = list(color = "#3498db", line = list(color = "white", width = 1)), opacity = 0.7) %>% layout(title = "AI Score Distribution", xaxis = list(title = "AI Score"), yaxis = list(title = "Count"))
```

### AI Label Breakdown
```{r}
ai_counts <- features %>% group_by(ai_label) %>% summarise(count = n(), .groups = "drop")
plot_ly(data = ai_counts, labels = ~ai_label, values = ~count, type = "pie", textinfo = "label+percent", marker = list(colors = c("#2c3e50", "#3498db", "#95a5a6", "#e74c3c"))) %>% layout(title = "AI Label Distribution")
```

### Top AI Leaders Table
```{r}
if(!is.null(features) && "ai_score" %in% names(features)) {
  output$ai_leaders_table <- renderDT({
    top_ai_leaders %>% 
      select(ticker, company_name, ai_score, innovation_score, revenue_growth, ai_label) %>% 
      mutate(
        ai_score = round(ai_score, 3), 
        innovation_score = round(innovation_score, 3), 
        revenue_growth = round(revenue_growth * 100, 1)
      ) %>% 
      datatable(
        colnames = c("Ticker", "Company", "AI Score", "Innovation", "Growth %", "Label"),
        options = list(pageLength = 10, dom = "Bfrtip", buttons = c("copy", "csv", "excel")),
        extensions = "Buttons",
        rownames = FALSE
      )
  })
} else {
  cat("⚠️ AI score data not available.\n")
}
```

Unicorn Watchlist
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### Unicorn Scatter Plot
```{r}
unicorn_data <- features %>% filter(unicorn_tier %in% c("Top Unicorn Candidate", "Emerging Unicorn Candidate", "Growth Candidate"))
plot_ly(data = unicorn_data, x = ~volatility, y = ~revenue_growth * 100, color = ~unicorn_tier, colors = c("Top Unicorn Candidate" = "#e74c3c", "Emerging Unicorn Candidate" = "#f39c12", "Growth Candidate" = "#3498db"), type = "scatter", mode = "markers", text = ~paste(company_name, "<br>Growth:", round(revenue_growth * 100, 1), "%<br>Volatility:", round(volatility, 3)), hoverinfo = "text", marker = list(size = 12, opacity = 0.7)) %>% layout(title = "Growth vs Volatility - Unicorn Candidates", xaxis = list(title = "Volatility"), yaxis = list(title = "Revenue Growth (%)"))
```

### Unicorn Watchlist Table
```{r}
unicorns %>% select(ticker, company_name, ai_score_aggressive, revenue_growth, volatility, unicorn_tier) %>% mutate(revenue_growth = round(revenue_growth * 100, 1), volatility = round(volatility, 3), ai_score_aggressive = round(ai_score_aggressive, 1)) %>% datatable(colnames = c("Ticker", "Company", "Aggressive AI", "Growth %", "Volatility", "Tier"), options = list(pageLength = 15, dom = "Bfrtip", buttons = c("copy", "csv", "excel")), extensions = "Buttons", rownames = FALSE)
```

Anomalies Detection
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### Anomaly Score Distribution
### Portfolio Anomalies
### Discovery Anomalies

```{r}
if(!is.null(anomaly_scores)) {
  plot_ly(data = anomaly_scores, x = ~anomaly_score, type = "histogram", nbinsx = 30, marker = list(color = "#e74c3c", line = list(color = "white", width = 1)), opacity = 0.7) %>% layout(title = "Anomaly Score Distribution", xaxis = list(title = "Anomaly Score (higher = more anomalous)"), yaxis = list(title = "Count"))

  anomaly_scores %>% filter(is_anomaly == TRUE, in_portfolio == TRUE) %>% left_join(features %>% select(ticker, company_name), by = "ticker") %>% select(ticker, company_name, anomaly_score, ai_score) %>% mutate(anomaly_score = round(anomaly_score, 3), ai_score = round(ai_score, 3)) %>% arrange(desc(anomaly_score)) %>% datatable(colnames = c("Ticker", "Company", "Anomaly Score", "AI Score"), options = list(pageLength = 10, dom = "Bfrtip", buttons = c("copy", "csv", "excel")), extensions = "Buttons", rownames = FALSE)

  anomaly_scores %>% filter(is_anomaly == TRUE, in_portfolio == FALSE) %>% left_join(features %>% select(ticker, company_name), by = "ticker") %>% select(ticker, company_name, anomaly_score, ai_score) %>% mutate(anomaly_score = round(anomaly_score, 3), ai_score = round(ai_score, 3)) %>% arrange(desc(anomaly_score)) %>% datatable(colnames = c("Ticker", "Company", "Anomaly Score", "AI Score"), options = list(pageLength = 10, dom = "Bfrtip", buttons = c("copy", "csv", "excel")), extensions = "Buttons", rownames = FALSE)
} else {
  cat("⚠️ Anomaly scores data not available for this run.\n")
}
```

Portfolio Comparison
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### AI Exposure Radar Chart
```{r}
if(!is.null(benchmark_ai)) {
  radar_plot_data <- data.frame(
  metric = c("AI Score", "AI Leaders %", "Growth", "Stability"),
  DUMAC = c(
    benchmark_ai$weighted_ai_score[benchmark_ai$name == "DUMAC Portfolio"],
    benchmark_ai$pct_ai_leaders[benchmark_ai$name == "DUMAC Portfolio"] / 100,
    benchmark_ai$avg_revenue_growth[benchmark_ai$name == "DUMAC Portfolio"],
    1 - benchmark_ai$avg_volatility[benchmark_ai$name == "DUMAC Portfolio"]
  ),
  SP500 = c(
    benchmark_ai$weighted_ai_score[benchmark_ai$name == "S&P 500"],
    benchmark_ai$pct_ai_leaders[benchmark_ai$name == "S&P 500"] / 100,
    benchmark_ai$avg_revenue_growth[benchmark_ai$name == "S&P 500"],
    1 - benchmark_ai$avg_volatility[benchmark_ai$name == "S&P 500"]
  ),
  NASDAQ = c(
    benchmark_ai$weighted_ai_score[benchmark_ai$name == "NASDAQ 100"],
    benchmark_ai$pct_ai_leaders[benchmark_ai$name == "NASDAQ 100"] / 100,
    benchmark_ai$avg_revenue_growth[benchmark_ai$name == "NASDAQ 100"],
    1 - benchmark_ai$avg_volatility[benchmark_ai$name == "NASDAQ 100"]
  )
)

plot_ly(type = 'scatterpolar', mode = 'lines+markers', fill = 'toself') %>%
  add_trace(r = as.numeric(radar_plot_data$DUMAC), theta = radar_plot_data$metric, name = "DUMAC Portfolio", line = list(color = "#2c3e50", width = 2), fillcolor = 'rgba(44, 62, 80, 0.3)') %>%
  add_trace(r = as.numeric(radar_plot_data$SP500), theta = radar_plot_data$metric, name = "S&P 500", line = list(color = "#3498db", width = 2), fillcolor = 'rgba(52, 152, 219, 0.3)') %>%
  add_trace(r = as.numeric(radar_plot_data$NASDAQ), theta = radar_plot_data$metric, name = "NASDAQ 100", line = list(color = "#e74c3c", width = 2), fillcolor = 'rgba(231, 76, 60, 0.3)') %>%
  layout(title = "AI Exposure Radar", polar = list(radialaxis = list(visible = TRUE, range = c(0, 1))))
} else {
  cat("⚠️ Benchmark AI data not available for radar chart.\n")
}
```

### Benchmark Comparison Table
```{r}
if(!is.null(benchmark_ai)) {
  benchmark_ai %>% select(name, weighted_ai_score, pct_ai_leaders, pct_ai_adopters, pct_ai_followers, pct_ai_laggards, active_share) %>% mutate(weighted_ai_score = round(weighted_ai_score, 3), across(starts_with("pct_"), ~ round(., 1)), active_share = round(active_share * 100, 1)) %>% datatable(colnames = c("Benchmark", "AI Score", "Leaders %", "Adopters %", "Followers %", "Laggards %", "Active Share %"), options = list(dom = "Bfrtip", buttons = c("copy", "csv", "excel")), extensions = "Buttons", rownames = FALSE)
} else {
  cat("⚠️ Benchmark AI data not available for this run.\n")
}
```

### S&P 500 AI by Sector
```{r}
if(!is.null(sector_ai)) {
  sector_ai %>% head(15) %>% select(TRBC_Industry, n_companies, weighted_ai, pct_ai_leaders) %>% mutate(weighted_ai = round(weighted_ai, 3), pct_ai_leaders = round(pct_ai_leaders, 1)) %>% datatable(colnames = c("Sector", "Companies", "AI Score", "Leaders %"), options = list(pageLength = 10, dom = "Bfrtip", buttons = c("copy", "csv", "excel")), extensions = "Buttons", rownames = FALSE)
} else {
  cat("⚠️ Sector AI data not available for this run.\n")
}
```

### Portfolio Concentration
```{r}
if(!is.null(portfolio_conc)) {
  portfolio_conc %>% 
    head(20) %>% 
    select(any_of(c("rank", "ticker", "company_name", "weight_pct", "cumulative_weight", "ai_label"))) %>%
    mutate(
      weight_pct = round(weight_pct, 1),
      cumulative_weight = round(cumulative_weight * 100, 1)
    ) %>% 
    datatable(
      colnames = c("Rank", "Ticker", "Company", "Weight %", "Cumulative %", "AI Label"),
      options = list(pageLength = 10, dom = "Bfrtip", buttons = c("copy", "csv", "excel")),
      extensions = "Buttons",
      rownames = FALSE
    )
} else {
  cat("⚠️ Portfolio concentration data not available.\n")
}
```

Company Deep Dive
=======================================================================

### 🔍 Select a Company
```{r}
company_choices <- setNames(features$ticker, paste(features$ticker, "-", features$company_name))
selectInput("company_select", "Search for a company:", choices = company_choices, selected = features$ticker[1], selectize = TRUE)
```

### Selected Company
```{r}
selected_company <- reactive({
  req(input$company_select)
  features %>% filter(ticker == input$company_select) %>% slice(1)
})

renderValueBox({
  company <- selected_company()
  valueBox(paste(company$ticker, "-", company$company_name), icon = "fa-building", color = "primary")
})
```

### AI Score Gauge
```{r}
renderPlotly({
  company <- selected_company()
  plot_ly(type = "indicator", mode = "gauge+number", value = company$ai_score, title = list(text = "AI Score"), gauge = list(axis = list(range = list(0, 1.5)), bar = list(color = "#2c3e50"), steps = list(list(range = c(0, 0.5), color = "#e74c3c"), list(range = c(0.5, 0.75), color = "#f39c12"), list(range = c(0.75, 1), color = "#3498db"), list(range = c(1, 1.5), color = "#2ecc71")), threshold = list(line = list(color = "red", width = 4), thickness = 0.75, value = company$ai_score)), number = list(suffix = " / 1.5")) %>% layout(margin = list(t = 50, b = 50))
})
```

### Innovation Score Gauge
```{r}
renderPlotly({
  company <- selected_company()
  plot_ly(type = "indicator", mode = "gauge+number", value = company$innovation_score, title = list(text = "Innovation Score"), gauge = list(axis = list(range = list(0, 1)), bar = list(color = "#3498db"), steps = list(list(range = c(0, 0.25), color = "#e74c3c"), list(range = c(0.25, 0.5), color = "#f39c12"), list(range = c(0.5, 0.75), color = "#3498db"), list(range = c(0.75, 1), color = "#2ecc71"))), number = list(suffix = " / 1.0")) %>% layout(margin = list(t = 50, b = 50))
})
```

### Key Metrics Table
```{r}
renderUI({
  company <- selected_company()
  tags$div(class = "panel panel-default",
    tags$div(class = "panel-heading", "Key Metrics"),
    tags$div(class = "panel-body",
      tags$table(class = "table table-condensed",
        tags$tr(tags$td("AI Label"), tags$td(strong(company$ai_label))),
        tags$tr(tags$td("Innovation Label"), tags$td(strong(company$innovation_label))),
        tags$tr(tags$td("Revenue Growth"), tags$td(paste0(round(company$revenue_growth * 100, 1), "%"))),
        tags$tr(tags$td("Volatility"), tags$td(round(company$volatility, 3))),
        tags$tr(tags$td("R&D Intensity"), tags$td(paste0(round(company$rd_intensity * 100, 1), "%"))),
        tags$tr(tags$td("Patent Activity"), tags$td(round(company$patent_activity, 0))),
        tags$tr(tags$td("Market Cap"), tags$td(paste0("$", format(round(company$market_cap / 1e9, 2), big.mark = ","), "B"))),
        tags$tr(tags$td("In Portfolio"), tags$td(ifelse(company$in_portfolio, "✅ Yes", "❌ No"))),
        tags$tr(tags$td("Unicorn Tier"), tags$td(ifelse(!is.na(company$unicorn_tier) & company$unicorn_tier != "Monitor", company$unicorn_tier, "N/A"))),
        tags$tr(tags$td("Anomaly"), tags$td(ifelse(company$is_anomaly, "⚠️ Detected", "✅ Normal")))
      )
    )
  )
})
```

Discovery Opportunities
=======================================================================

```{r}
# Discovery table with AI Score from features
if(!is.null(discovery_full) && !is.null(features) && "ai_score" %in% names(features)) {
  
  # Perform join and handle potential column name conflicts
  discovery_joined <- discovery_full %>%
    filter(discovery_tier == "Tier 1: Top 10 Opportunities") %>%
    left_join(features %>% select(ticker, company_name, ai_score), by = "ticker")
  
  # Check what columns exist after join
  if("ai_score" %in% names(discovery_joined)) {
    # Simple case - ai_score exists directly
    discovery_joined <- discovery_joined %>%
      arrange(combined_rank) %>%
      select(combined_rank, ticker, company_name, ai_score, discovery_tier) %>%
      mutate(ai_score = round(ai_score, 3))
  } else if("ai_score.y" %in% names(discovery_joined)) {
    # Case where join created ai_score.x and ai_score.y
    discovery_joined <- discovery_joined %>%
      arrange(combined_rank) %>%
      select(combined_rank, ticker, company_name, ai_score = ai_score.y, discovery_tier) %>%
      mutate(ai_score = round(ai_score, 3))
  } else {
    # No ai_score found - show message
    cat("⚠️ AI Score column not found after join.\n")
    discovery_joined <- discovery_joined %>%
      arrange(combined_rank) %>%
      select(combined_rank, ticker, discovery_tier) %>%
      mutate(ai_score = NA)
  }
  
  # Create datatable
  discovery_joined %>%
    datatable(
      colnames = c("Rank", "Ticker", "Company", "AI Score", "Tier"),
      options = list(pageLength = 10, dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel')),
      extensions = 'Buttons',
      rownames = FALSE
    ) %>%
    formatStyle(
      'ai_score',
      background = styleColorBar(c(0, 1.5), 'lightblue'),
      backgroundSize = '100% 90%',
      backgroundRepeat = 'no-repeat'
    )
    
} else {
  cat("⚠️ Discovery opportunities data not available for this run.\n")
}  
```

Methodology
=======================================================================

```{r, echo=FALSE, results='asis'}
cat("
### AI Score Definition (CORRECTED)
- R&D Intensity: 30% (calculated as R&D Expense / Revenue)
- Patent Activity: 30%  
- Revenue Growth: 20% (from historical fiscal year data)
- Stability (Inverse Volatility): 20%

### Aggressive AI Score (Unicorn Hunting)
- R&D Intensity: 25%
- Patent Activity: 20%
- Revenue Growth: 40%
- Stability: 15%

### Unicorn Candidate Criteria
- Top 30% revenue growth
- Top 30% volatility
- Positive R&D intensity
- Not a standard AI Leader

### Anomaly Detection
- Isolation Forest algorithm (100 trees)
- Top 10% threshold
- Features: R&D, patents, growth, volatility, market cap, AI score, innovation score

### Data Sources
- Refinitiv: Financial history, daily ratios, benchmark constituents
- USPTO: Patent data with AI CPC codes (G06N, G06K, G06F, G10L, G05B, G16H)
- DUMAC: Portfolio holdings via ISIN matching

### Run Information (CORRECTED)
- Run Date: 2026-04-01
- Run ID: run_20260401_162940
- Total Companies: ", total_companies, "
- AI Leaders: ", ai_leaders, "
- Unicorn Candidates: ", unicorn_count, "
- Imputed Companies: 85 (47.0%)

### Key Fixes Applied
- R&D Intensity now uses Revenue instead of Market Cap
- Revenue Growth uses historical fiscal year data (not placeholder)
- NVIDIA corrected from AI Laggard (0.500) to AI Leader (1.125)
- MSFT, AAPL correctly identified as AI Leaders
")
```
